Investigating The Fleishman Effect : Subjective Evaluations of Financial Satisfaction in the US General Social Survey

### 2023-03-13 outputs/paper/paper3.qmd
Minor formatting updates

```{r}
#| message: false
#| echo: false
#| warning: false
#| label: fig-socialclass-compare
#| fig-cap: "Financial comparison responses for each social class"

@@

generate_compare_bar_graph(
  ggplot_data = 
    survey_data_2021 |>
    filter(!is.na(social_class1), !is.na(financial_compare)) |>
    group_by(social_class1, financial_compare) |>
    count() |>
    ungroup() |>
    group_by(social_class1) |>
    mutate(pct = percent(n / sum(n), digit = 1)) |>
    ggplot(aes(x = social_class1, y = pct, fill = financial_compare)),
  angle = 45,
  hjust = 1,
  nrow = 2,
  xlabel = "Social Class (6-Bands)",
  ylabel = "Percentage of Responses",
  fill_label = "Comparing to Others"
)

@@

(fig-2021-degree-financial) shows that respondents with post-secondary education experience better changes in financial situation, with 50% of respondents with graduate degrees reporting that their financial situation is "getting better". Subsetting these reference groups by their area of study, and whether or not they regret their major, could provide more information on how the different returns-on-investment on different degrees change over time, as shown by The Washington Post's reporting on the Federal Reserve Survey of Household Economics and Decisionmaking [@collegeMajors].

@@

#### Cross-Referencing

Connecting our results with US census data to check for representativeness in respondents answers could strengthen interpretations, and help to understand any discrepancies in self-reported data. This would also help us understand how the new methodology implemented by the GSS in 2021 may have influenced self-reported results.

Bringing in other macroeconomic indicators, such as inflation and capital market trends, can also provide an extra dimension to understanding how wealth has evolved and been impacted over time.

-   Additional financial variables in survey for analysis

>>>>

```{r}
#| message: false
#| echo: false
#| warning: false
#| label: fig-socialclass-compare
#| fig-cap: "Financial comparison responses for each social class (6-bands)"

@@

generate_compare_bar_graph(
  ggplot_data = 
    survey_data_2021 |>
    filter(!is.na(social_class1), !is.na(financial_compare)) |>
    group_by(social_class1, financial_compare) |>
    count() |>
    ungroup() |>
    group_by(social_class1) |>
    mutate(pct = percent(n / sum(n), digit = 1)) |>
    ggplot(aes(x = social_class1, y = pct, fill = financial_compare)),
  angle = 45,
  hjust = 1,
  xlabel = "Social Class (6-Bands)",
  ylabel = "Percentage of Responses",
  fill_label = "Comparing to Others"
) +
theme(legend.position=NULL)

@@

@fig-2021-degree-financial shows that respondents with post-secondary education experience better changes in financial situation, with 50% of respondents with graduate degrees reporting that their financial situation is "getting better". Obtaining more details on these reference groups by their area of study, and whether or not they regret their major, could provide more information on how the different returns-on-investment on different degrees change over time, as shown by The Washington Post's reporting on the Federal Reserve Survey of Household Economics and Decision Making [@collegeMajors].

@@

#### Incorporate Additional Data Sources

Additional data sources can be used to explore additional trends in attitudes towards financial wellness. First, we can connecting our results with US census data to check for representativeness in respondents answers, and to understand any discrepancies in self-reported data. This would also help us understand how the new methodology implemented by the GSS in 2021 may have influenced self-reported results. Also, bringing in other macroeconomic indicators, such as inflation and capital market trends, can provide an extra dimension to understanding how wealth has evolved and been impacted over time.
